\pageId{gettingstarted}

\begin{itemize}

  \item
    You can \href[Download]{http://sourceforge.net/project/showfiles.php?group_id=221375}
    one of the SnuggleTeX ZIP distributions from SourceForge.net.
    As of SnuggleTeX 1.1.0, these comes in two flavours:

    \begin{enumerate}
      \item \verb|snuggletex-n.n.n-basic.zip| is a basic binary distribution containing
        everything you need for SnuggleTeX's core functionality, allowing
        you to convert LaTeX to XHTML/MathML. No further JAR files
        are required for this.

      \item \verb|snuggletex-n.n.n-full.zip| is the full distribution containing
        all SnuggleTeX modules, all required dependencies and the project sources.
        Use this one if you want to do convert LaTeX to XHTML+images, or use
        the up-conversion module to generate Content MathML and/or Maxima syntax.
        Always use this distribution if you wish to use this additional
        functionality.
    \end{enumerate}

  \item
    If you are using \href[Apache Maven]{http://maven.apache.org/} then you may
    obtain SnuggleTeX artifacts (starting from 1.1.0-beta1) from the following repository:
\begin{verbatim}<repository>
  <id>www.ph.ed.ac.uk-releases</id>
  <url>http://www.ph.ed.ac.uk/maven2</url>
</repository>\end{verbatim}
    where you will find the following:
\begin{verbatim}<dependency>
  <groupId>uk.ac.ed.ph.snuggletex</groupId>
  <artifactId>snuggletex-core</artifactId>
  <version>...</version>
</dependency>
<dependency>
  <groupId>uk.ac.ed.ph.snuggletex</groupId>
  <artifactId>snuggletex-upconversion</artifactId>
  <version>...</version>
</dependency>
<dependency>
  <groupId>uk.ac.ed.ph.snuggletex</groupId>
  <artifactId>snuggletex-jeuclid</artifactId>
  <version>...</version>
</dependency>\end{verbatim}

  \item See the table below for a guide of which JARs you will need for
    the main types of SnuggleTeX activity.

\end{itemize}

\subsection*{List of JARs}

{\bf Note:} All of the JARs in the full SnuggleTeX distribution
will have version numbers in their names. I have omitted these in
the table below.

\begin{tabular}{|c|c|l|l|}
\hline
Activity &
Suggested Distribution &
Required at Compile Time &
Required at Run Time \\
\hline
Convert LaTeX to basic XHTML+MathML
as either DOM or simple web pages &
Basic &
\verb|snuggletex-core.jar| &
\verb|snuggletex-core.jar| \\
\hline
Additionally generate Content MathML and/or Maxima input\newline
or convert the output from ASCIIMathML to Content MathML &
Full &
\verb|snuggletex-core.jar|\newline
\verb|snuggletex-upconversion.jar| &
\verb|snuggletex-core.jar|\newline
\verb|snuggletex-upconversion.jar|\newline
\verb|saxon9-jar|\newline
\verb|saxon9-dom.jar| \\
\hline
Generate legacy XHTML+images web pages &
Full &
\verb|snuggletex-core.jar|\newline
\verb|snuggletex-jeuclid.jar| &
\verb|snuggletex-core.jar|\newline
\verb|snuggletex-jeuclid.jar|\newline
\verb|jeuclid-core.jar|\newline
\verb|batik-dom.jar|\newline
\verb|batik-ext.jar|\newline
\verb|batik-util.jar|\newline
\verb|batik-xml.jar|\newline
\verb|commons-io.jar|\newline
\verb|commons-logging.jar|\newline
\verb|xml-apis.jar| (*)\newline
\verb|xml-apis-ext.jar|\newline
\verb|xmlgraphics-commons.jar| \\
\hline
\end{tabular}

\subsubsection*{Notes}
\begin{itemize}
  \item (*) Not required for Java 6 and above.
  \item In all cases, we recommend using \verb|saxon9.jar| and \verb|saxon9-dom.jar| anyway,
    which can be found in the full distribution.
\end{itemize}
