\pageId{overview}

SnuggleTeX is a free and open-source Java library for converting fragments
of LaTeX to XML (usually XHTML + MathML).

\begin{itemize}

\item
  SnuggleTeX can convert simple LaTeX documents consisting of a mixture of text
  and math mode LaTeX into XHTML with embedded MathML.

\item
  More simply, SnuggleTeX can convert math mode LaTeX to MathML, generating Presentation
  MathML by default.

\item
  As of SnuggleTeX 1.1.0, SnuggleTeX can also attempt to
  ``\href[semantically enrich]{docs://upconversion}'' or
  ``up-conver'' the Presentation MathML it creates, additionally generating
  Content MathML and/or \href[Maxima]{http://maxima.sourceforge.net/} input
  formats if it can make enough sense of the LaTeX input.  (This is currently experimental work
  aimed primarily at secondary/early tertiary UK Education contexts!)

\item
  SnuggleTeX can output either a DOM fragment, an XML string fragment, or create
  a full standalone web page of various types.

\item
  Web page outputs can be configured in various ways and SnuggleTeX provides
  a number of useful web page templates that can be used to target certain browser
  and deployment options.

\item
  SnuggleTeX has optional features for converting the resulting MathML to images
  (using the JEuclid library) and can additionally attempt to convert very
  simple MathML expressions into a mixture of XHTML and CSS.

\item
  Outputs can be fully standalone (e.g. with all CSS styling done inline) to enable
  XML fragments to be imported into other XML applications and/or systems
  which support XHTML+MathML.

\item
  Error reporting is configurable and error messages are internationalisable and
  provide detailed contextual information.

\item
  SnuggleTeX supports \verb|\newcommand| and \verb|\newenvironment| and
  friends, making it easy to create custom commands and environments within LaTeX.
  (It is also possible to define new commands and environments via Java.)

\item
  SnuggleTeX (1.1.0 and above) also includes some experimental utility code to convert the raw MathML
  generated by \href[ASCIIMathML]{http://www1.chapman.edu/~jipsen/asciimath.html}
  to Content MathML and Maxima notation by hooking into the semantic enrichment process.

\end{itemize}
