\pageId{features}

\section*{Features}

\begin{itemize}

  \item SnuggleTeX is a 100\% Java library with no dependencies on any other Java libraries
        (at least for normal use).

  \item SnuggleTeX can easily convert a good subset of (media-agnostic) LaTeX
        into XML (XHTML + MathML).

  \item SnuggleTeX can output either a DOM fragment, an XML fragment or a full
        standalone web page.

  \item Web page outputs can be configured in various ways and a there are a
        number of preset "page types" that support the most common ways that XHTML+MathML
        content can be deployed on the web.

  \item Outputs can be fully standalone (e.g. with all CSS styling done inline) to enable
        XML fragments to be imported into other XML applications and/or systems
        which support XHTML+MathML.

  \item Error reporting is configurable and error messages are internationalisable and
        provide detailed contextual information.

  \item SnuggleTeX supports \verb|\newcommand| and \verb|\newenvironment| and
        friends, making it easy to create custom commands and environments. There are
        also lower-level Java hooks for defining new commands and environments.

  \item SnuggleTeX has optional parser settings for inferring limited semantics in
        certain mathematical expressions, such as automatically fencing matched
        brackets, grouping infix operators and inserting "apply function" and
        "invisible times" operators into simple algebraic expressions.

\end{itemize}
