\pageId{usecases}

\section*{Use Cases --- Why Use SnuggleTeX?}

There are a healthy number of tools which have functionality related to SnuggleTeX,
which can make it hard to decide which tool bits fits your given requirements.
Like all tools, SnuggleTeX has its relative strengths and weaknesses that you
should consider:

\begin{itemize}

  \item SnuggleTeX was originally developed to support
        \href[Aardvark]{http://www.ph.ed.ac.uk/elearning/projects/aardvark/}
        in order to facilitate the conversion of fragments of LaTeX written by
        academics into XML tree branches. Another example of this type of use
        might be a kind of LaTeX-based Wiki, where SnuggleTeX could be used at
        some point in the LaTeX to XHTML conversion pipeline.

  \item SnuggleTeX is 100\% Java with minimal (usually no) dependencies on
        other libraries so can be easily integrated into a Java software
        development project as a library for converting LaTeX to XML.

  \item SnuggleTeX can also be used to generate
        \href[``legacy'' web pages]{outputs.html#legacy}
        where mathematical formulae are represented by HTML + CSS (if suitably
        simple) and/or images. (This uses the open-source
        \href[JEuclid]{http://jeuclid.sourceforge.net} library.)

  \item SnuggleTeX was \emph{not} intended to be a standalone tool that you
        could throw complete LaTeX documents at and have them converted to web
        pages. Other tools do this type of thing very well, such as
        \href[TeX4ht]{http://www.cse.ohio-state.edu/~gurari/TeX4ht/}.

  \item SnuggleTeX supports a pragmatic subset of LaTeX but does not include anything
        that is particularly paper- or page-specific. It also currently doesn't
        do cross-referencing or numbering. Other tools might therefore be a
        better fit for these types of requirements.

  \item SnuggleTeX's parser pretends that TeX never happened and may behave slightly
        differently to what experienced LaTeX users might expect. Novice LaTeX users
        will not notice any difference and might actually find the error
        messages provided here more useful.

  \item SnuggleTeX's web page outputs are highly configurable and make it relatively
        easy to create MathML-enabled pages that will work across a range of
        browser platforms. Hooks are available to customise the web page outputs;
        these require a knowledge of XSLT.

\end{itemize}
