\pageId{xmlCommands}

\section*{XML-related Commands}

SnuggleTeX provides a few custom commands to make it
easy to do certain XML-related tasks, which can be quite
useful if you are generating elements outwit the usual
XHTML and/or MathML.

\subsection*{Creating Custom XML Elements}

You can ask SnuggleTeX to create custom XML using the
\verb|\xmlBlockElement| and \verb|\xmlInlineElement|
commands. Both output exactly the same XML elements, however the former will
output the XML as a new ``block'' whereas the latter will output the XML
``inline'' with whatever surrounds it.

Both commands take 3 required arguments, plus an
optional one to allow you to set XML attributes
(see below). The required arguments are as follows:

\begin{enumerate}
  \item Namespace URI. This must be a valid URI, otherwise
    error \verb|TDEX04| will be recorded. 
    (Note that this argument is parsed in \verb|LR| mode
    rather than \verb|VERBATIM| mode so as to allow you to
    parametrise it, if required.)
  \item Element qName (qualified name), which will be of
    the form \verb|prefix:localName| or just
    \verb|localName|. An invalid qName will result in
    error \verb|TDEX01|.
  \item Element content
\end{enumerate}

If you are generating a lot of XML elements belonging
to a particular namespace, you will probably want to
define macros (either via \verb|\newcommand| or
through the Java API) that fill in more of the details.

\subsubsection*{Example}

\begin{verbatim}
\newcommand{\xhtmlBlockElement}[2][]
  {\xmlBlockElement[#1]{http://www.w3.org/1999/xhtml}{#2}{#3}}
\xhtmlBlockElement{hr}{}
\end{verbatim}

This generates an XHTML \verb|<hr/>| element:

\newcommand{\xhtmlBlockElement}[3][]
  {\xmlBlockElement[#1]{http://www.w3.org/1999/xhtml}{#2}{#3}}
\xhtmlBlockElement{hr}{}

\subsection*{XML Attributes}

The \verb|\xmlBlockElement| and \verb|\xmlInlineElement| commands both take
optional arguments that allow XML attributes to be specified. This is
done using a number of \verb|\xmlAttr| commands. These take 3 arguments
--- namespace URI, qName and value --- in the same way as above. Using
an \verb|\xmlAttr| in any other place in a document will record a
\verb|TDEX02| error.

\subsection*{XML Names}

It is sometimes useful to be able to enforce that a particular input
is a valid XML name. This can be done with the \verb|\xmlName| command.
It takes a single argument and returns it unchanged, recording a
\verb|TDEX03| error if the name is invalid.
